Make manuscript figures

### 2022-06-11 scripts/R/make_manuscript_figures.rmd
add y=x line to simulation example figure

example_data_lo_h2 <- example_simulation_results %>% filter(H2 == 0.15, alpha == 0.1)
min_runID <- min(example_data_lo_h2$runID)
example_data_lo_h2 <- example_data_lo_h2 %>% filter(runID == min_runID)
example_data_hi_h2 <- example_simulation_results %>% filter(H2 == 0.75, alpha == 0.1)
min_runID <- min(example_data_hi_h2$runID)
example_data_hi_h2 <- example_data_hi_h2 %>% filter(runID == min_runID)
example_data <- rbind(example_data_lo_h2, example_data_hi_h2) %>% rename("label" = "sample", "Heritability" = "H2")

@@

# Plot trait value accuracy
p1 <- ggplot(data = example_data, aes(x = h, y = h.MWA)) +
      geom_point() +
      facet_grid(. ~ Heritability, labeller = "label_both") + 
      shared_theme +
      labs(x = "Simulated host part of trait", y = "Estimated non-pathogen\npart of trait")

>>>>

example_data_lo_h2 <- example_simulation_results %>% filter(H2 == 0.15, alpha == 0.1)
selected_runID <- max(example_data_lo_h2$runID)
example_data_lo_h2 <- example_data_lo_h2 %>% filter(runID == selected_runID)
example_data_hi_h2 <- example_simulation_results %>% filter(H2 == 0.75, alpha == 0.1)
selected_runID <- max(example_data_hi_h2$runID)
example_data_hi_h2 <- example_data_hi_h2 %>% filter(runID == selected_runID)
example_data <- rbind(example_data_lo_h2, example_data_hi_h2) %>% rename("label" = "sample", "Heritability" = "H2")

@@

# Plot trait value accuracy
p1 <- ggplot(data = example_data, aes(x = h, y = h.MWA)) +
      geom_point() +
      facet_wrap(. ~ Heritability, labeller = "label_both") + 
      geom_abline(intercept = 0, slope = 1) + 
      shared_theme +
      labs(x = "Simulated host part of trait", y = "Estimated non-pathogen\npart of trait")
